Reply To Examiners

### 2014-04-26 answer_thesis_examiner/chap2.tex
auto

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
3 & 12 & Similarly speaking, & Similarly, \\
3 & 19 & criteria & criterion \\ 
4 & 14 & MMSE criteria & MMSE criterion \\
6 & 9 & Last but certainly not least, & Thirdly, \\ 
6 & 9 & such a framework allow & such a framework allows \\
9 & 7 & multidimensional & Multi-dimensional \\
10 & 12 & The model os & The model is \\
11 & 28 & chapter 5 & Chapter 5 \\
12 & 6 & chapter 6 & Chapter 6 \\
22 & 15 & RadarSat & RadarSat-2 \\
24 & 14 & SVM & SVM (Support Vector Machine) \\
35 & 6-7 & Rician distribution [48]... & Rician distribution [48]. \\
35 & 11 & back scattering & backscattering \\
36 & 10 & literatured & literatures \\
37 & -2 & Proposed bu & proposed by \\
39 & 4 & dependence & dependency \\
44 & -1 & The nature of SAR is ... heteroskedastic heterogeneously & the sentence is rephrased \\
\end{longtable}

>>>>

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
3 & 12 & Similarly speaking, & Similarly, \\
3 & 19 & criteria & criterion \\ 
4 & 14 & MMSE criteria & MMSE criterion \\
6 & 9 & Last but certainly not least, & Thirdly, \\ 
6 & 9 & such a framework allow & such a framework allows \\
9 & 7 & multidimensional & Multi-dimensional \\
10 & 12 & The model os & The model is \\
11 & 28 & chapter 5 & Chapter 5 \\
12 & 6 & chapter 6 & Chapter 6 \\
22 & 15 & RadarSat & RadarSat-2 \\
24 & 14 & SVM & SVM (Support Vector Machine) \\
35 & 6-7 & Rician distribution [48]... & Rician distribution [48]. \\
35 & 11 & back scattering & backscattering \\
36 & 10 & literatured & literatures \\
37 & -2 & Proposed bu & proposed by \\
39 & 4 & dependence & dependency \\
44 & -1 & The nature of SAR is ... heteroskedastic heterogeneously & the sentence is rephrased \\
46 & 4 & most known common & most commonly known \\
56 & 6 & POLSAR And & POLSAR. And \\
65 &5,7 & an homogeneous area & a homogeneous area \\
77 & 3 & the objective then is & the objective is \\
77 & 5,6 & it has already been proven & it has already been proven [?] \\
87 & -1 & Fig 5.6a & Fig 5.6. \\
89 & - & Figure 5.6 - subtitle (a) & (a) is removed \\
91 & - & Figure 5.8: Legends are too small to read & They are enlarged \\
95 & - & Figure 5.12 & Use the same scale for  y axis (i.e MSE 0:1) across all the plots \\
103 & 22 & related to the ENL index. over & related to the ENL index over \\
104 & 13 & Equation 5.3.2.1 & The number is corrected to (?) \\
109 & 8 & Figs. 5.21c and 5.21d allows & Fig 5.21(a) and Fig 5.21(d) allow \\
112 & 13 & these smaller requirements & these requirements \\
132 & 9 & evaluation criteria & evaluation criterion
\end{longtable}

\textbf{Overall Comments \& Replies}

In general, I wish to express my appreciation towards Examiner No. 2 for his careful, detailed and concise review.
I am amazed by the fact that the Examiner is able to precisely summarize the long thesis into a single sentence.
I also feel indebted to the Examiner with his suggestion to extract out and submit portions of this thesis as scientific papers for peer review.

=====
